---
output: rmarkdown::github_document
---

`maRalago` : Is Trump At Mar-a-Lago (and more)

See if Trump is at Mar-a-Lago and also retreive total trips/costs to Mar-a-Lago
as well as a list of programs with unit costs to assist in derivation of what the
narcisstic waste of money could be used to fund or keep funding.

It relies on a Google spreadsheet maintaind by the Center for American Progress Action
Fund which was discovered after seeing   [https://istrumpatmaralago.org/](https://istrumpatmaralago.org/).

The following functions are implemented:

- `could_pay_for`:	Retrieve program names, descriptions and unit costs
- `download_maralago`:	Download the full Excel file
- `is_there`:	Is Trump at Mar-a-Lago?
- `trips_info`:	Retrieve Trip Data (with costs)

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/maRalago")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

### Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(maRalago)

# current verison
packageVersion("maRalago")

is_there()

trips_info()

could_pay_for()
```
